check_effect_transformation

### 2021-09-22 supplementary/distance-computation/real-data/algo2-cust600-assimilateHPC.Rmd
adding new analaysis

  all_files = list.files(path = paste0("data/algo2/"), 
                         pattern = ".rds")

@@

  all_files_path <- paste0("data/algo2/",
                           all_files)

@@

  write_rds(all_data, paste0("data/algo2-rawdata-wpd.rds"))
```

>>>>

  all_files = list.files(path = paste0("../../../data/algo2-600cust/"), 
                         pattern = ".rds")

@@

  all_files_path <- paste0("../../../data/algo2-600cust/",
                           all_files)

@@

  write_rds(all_data, paste0("../../../data/algo2-cust600-wpd-rawdata.rds"))
```

### 2021-09-22 supplementary/distance-computation/simulation-data/D4_I5_C2.Rmd
adding new analaysis

---
title: "2 designs and 5 iterations and categorty changes across 1 granularity (g3 and g1 categories const) "
author: "Sayani Gupta"
output:
  bookdown::pdf_book:
    #base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    fig_caption: yes
    dev: "pdf"
    keep_tex: yes
    toc: false
    cache: TRUE
---

@@

```{r change-var, echo=TRUE}
t = 300
n <- seq(0, t, 1)
g1 <- n %%2
g2 <- n %%3
g3 <- n %%5
mu1= c(0, 0) # mean of cat of g1
mu2 = c(7, 5, 1)# mean of cat of g2
mu3 = c(0, 0, 0, 0, 0) # mean of cat of g3
```

@@

# _Granularities design_
```{r}
design = c("design-1", "design-2")
g1 = c("no", "no")
g2 = c("no", "yes")
g3 = c("no", "no")
table <- tibble(design, g1, g2, g3) %>% kable()
table

@@

design1 = distributional::dist_normal(g1_dnull + g2_dnull + g3_dnull)
design2 = distributional::dist_normal(g1_dnull + g2_dvary + g3_dnull)
#design3 = distributional::dist_normal(g1_dnull + g2_dvary + g3_dnull)
#design4 = distributional::dist_normal(g1_dvary + g2_dvary + g3_dnull)
#design5 = distributional::dist_normal(g1_dvary + g2_dvary + g3_dvary)

data_bind <- tibble::tibble(
index = t,
g1 = g1,
g2 = g2,
g3 = g3,
design1 = distributional::generate(design1, times = 1) %>% unlist(),
design2 = distributional::generate(design2, times = 1) %>% unlist(),
#design3 = distributional::generate(design3, times = 1) %>% unlist(),
#design4 = distributional::generate(design4, times = 1) %>% unlist(),
#design5 = distributional::generate(design5, times = 1) %>% unlist()
) %>% 
  pivot_longer(-c(1, 2, 3, 4), names_to = "design", values_to = "sim_data")

@@

groups = dist_mat%>% clust_gran(kopt = 2 )
pred_group = paste("design",groups$group,sep = "") %>% as.factor()
actual_group = as.factor(bind_data_iter_tsibble %>%as_tibble %>% select(customer_id, design) %>% distinct() %>% pull(design))

@@

groups = dist_mat %>% 
  clust_gran(kopt = 2 )

>>>>

---
title: "4 designs and 5 iterations and categorty changes across 2 granularities (g3 categories const) "
author: "Sayani Gupta"
output:
  bookdown::pdf_book:
    #base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    fig_caption: yes
    dev: "pdf"
    keep_tex: yes
    toc: false
    cache: TRUE
---

@@

```{r change-var, echo=TRUE}
t = 300
n <- seq(0, t, 1)
g1 <- n %%2
g2 <- n %%3
g3 <- n %%5
mu1= c(0, 2) # mean of cat of g1
mu2 = c(7, 5, 1)# mean of cat of g2
mu3 = c(0, 0, 0, 0, 0) # mean of cat of g3
```

@@

# _Granularities design_
```{r}
design = c("design-1", "design-2", "design-3", "design4")
g1 = c("no", "no", "yes", "yes")
g2 = c("no", "yes", "no", "yes")
g3 = c("no", "no", "no", "no")
table <- tibble(design, g1, g2, g3) %>% kable()
table

@@

design1 = distributional::dist_normal(g1_dnull + g2_dnull + g3_dnull)
design2 = distributional::dist_normal(g1_dvary + g2_dnull + g3_dnull)
design3 = distributional::dist_normal(g1_dnull + g2_dvary + g3_dnull)
design4 = distributional::dist_normal(g1_dvary + g2_dvary + g3_dnull)
#design5 = distributional::dist_normal(g1_dvary + g2_dvary + g3_dvary)

data_bind <- tibble::tibble(
index = t,
g1 = g1,
g2 = g2,
g3 = g3,
design1 = distributional::generate(design1, times = 1) %>% unlist(),
design2 = distributional::generate(design2, times = 1) %>% unlist(),
design3 = distributional::generate(design3, times = 1) %>% unlist(),
design4 = distributional::generate(design4, times = 1) %>% unlist(),
#design5 = distributional::generate(design5, times = 1) %>% unlist()
) %>% 
  pivot_longer(-c(1, 2, 3, 4), names_to = "design", values_to = "sim_data")

@@

groups = dist_mat%>% clust_gran(kopt = 4)
pred_group = paste("design",groups$group,sep = "") %>% as.factor()
actual_group = as.factor(bind_data_iter_tsibble %>%as_tibble %>% select(customer_id, design) %>% distinct() %>% pull(design))

@@

groups = dist_mat %>% 
  clust_gran(kopt = 4)

### 2021-09-22 supplementary/distance-computation/simulation-data/D5_I5_C3.Rmd
adding new analaysis

---
title: "4 designs and 5 iterations and categorty changes across 2 granularities (g3 categories const) "
author: "Sayani Gupta"
output:
  bookdown::pdf_book:
    #base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    fig_caption: yes
    dev: "pdf"
    keep_tex: yes
    toc: false
    cache: TRUE
---

@@

```{r change-var, echo=TRUE}
t = 300
n <- seq(0, t, 1)
g1 <- n %%2
g2 <- n %%3
g3 <- n %%5
mu1= c(0, 2) # mean of cat of g1
mu2 = c(7, 5, 1)# mean of cat of g2
mu3 = c(0, 0, 0, 0, 0) # mean of cat of g3
```

@@

# _Granularities design_
```{r}
design = c("design-1", "design-2", "design-3", "design4")
g1 = c("no", "no", "yes", "yes")
g2 = c("no", "yes", "no", "yes")
g3 = c("no", "no", "no", "no")
table <- tibble(design, g1, g2, g3) %>% kable()
table

@@

```{r generate-design}
generate_design <- function(t, mu1, mu2, mu3){
t <- seq(0, t, 1)
g1 <- t %%2
g2 <- t %%3
g3 <- t %%5

@@

design1 = distributional::dist_normal(g1_dnull + g2_dnull + g3_dnull)
design2 = distributional::dist_normal(g1_dvary + g2_dnull + g3_dnull)
design3 = distributional::dist_normal(g1_dnull + g2_dvary + g3_dnull)
design4 = distributional::dist_normal(g1_dvary + g2_dvary + g3_dnull)
#design5 = distributional::dist_normal(g1_dvary + g2_dvary + g3_dvary)

data_bind <- tibble::tibble(
index = t,
g1 = g1,
g2 = g2,
g3 = g3,
design1 = distributional::generate(design1, times = 1) %>% unlist(),
design2 = distributional::generate(design2, times = 1) %>% unlist(),
design3 = distributional::generate(design3, times = 1) %>% unlist(),
design4 = distributional::generate(design4, times = 1) %>% unlist(),
#design5 = distributional::generate(design5, times = 1) %>% unlist()
) %>% 
  pivot_longer(-c(1, 2, 3, 4), names_to = "design", values_to = "sim_data")

@@

@@

groups = dist_mat%>% clust_gran(kopt = 4)
pred_group = paste("design",groups$group,sep = "") %>% as.factor()
actual_group = as.factor(bind_data_iter_tsibble %>%as_tibble %>% select(customer_id, design) %>% distinct() %>% pull(design))

@@

# _Cluster designs: distance using js distance between categories_

```{r js}
dist_mat_g1 <- bind_data_iter_tsibble %>%
  scale_gran(method = "robust", response = "sim_data") %>%
  dist_gran(gran1 = "g1", response= "sim_data")

@@

groups = dist_mat %>% 
  clust_gran(kopt = 4)

>>>>

---
title: "5 designs and 5 iterations and 3 granularities all of whose categories change"
author: "Sayani Gupta"
date: "15/09/2021"
output:
  bookdown::pdf_book:
    #base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    fig_caption: yes
    dev: "pdf"
    keep_tex: yes
    toc: false
    cache: TRUE
---

@@

```{r change-var, echo=TRUE}
t = 300
n <- seq(0, n, 1)
g1 <- n %%2
g2 <- n %%3
g3 <- n %%5
mu1= c(0, 2)
mu2 = c(7, 5, 1)
mu3 = c(1, 2, 5, 3, 1)
```

@@

# _Granularities design_
```{r}
design = c("design-1", "design-2", "design-3", "design4", "design5")
g1 = c("no", "yes", "no", "no", "yes")
g2 = c("no", "no", "yes", "no", "yes")
g3 = c("no", "no", "no", "yes", "yes")
table <- tibble(design, g1, g2, g3) %>% kable()
table

@@

```{r}
generate_design <- function(t, mu1, mu2, mu3){

t <- seq(0, t, 1)
g1 <- t %%2
g2 <- t %%3
g3 <- t %%5

@@

design1 = distributional::dist_normal(g1_dnull + g2_dnull + g3_dnull)
design2 = distributional::dist_normal(g1_dvary + g2_dnull + g3_dnull)
design3 = distributional::dist_normal(g1_dnull + g2_dvary + g3_dnull)
design4 = distributional::dist_normal(g1_dnull + g2_dnull + g3_dvary)
design5 = distributional::dist_normal(g1_dvary + g2_dvary + g3_dvary)

data_bind <- tibble::tibble(
index = t,
g1 = g1,
g2 = g2,
g3 = g3,
design1 = distributional::generate(design1, times = 1) %>% unlist(),
design2 = distributional::generate(design2, times = 1) %>% unlist(),
design3 = distributional::generate(design3, times = 1) %>% unlist(),
design4 = distributional::generate(design4, times = 1) %>% unlist(),
design5 = distributional::generate(design5, times = 1) %>% unlist()
) %>% 
  pivot_longer(-c(1, 2, 3, 4), names_to = "design", values_to = "sim_data")

@@

t = 300
mu1= c(0, 2)
mu2 = c(7, 5, 1)
mu3 = c(1, 2, 5, 3, 1)

@@

groups = dist_mat%>% clust_gran(kopt = 5)
pred_group = paste("design",groups$group,sep = "") %>% as.factor()
actual_group = as.factor(bind_data_iter_tsibble %>%as_tibble %>% select(customer_id, design) %>% distinct() %>% pull(design))

@@

# _Cluster designs: distance using js distance between categories (robust scaling)_

```{r js-robust}
dist_mat_g1 <- bind_data_iter_tsibble %>%
  scale_gran(method = "robust", response = "sim_data") %>%
  dist_gran(gran1 = "g1", response= "sim_data")

@@

groups = dist_mat %>% 
  clust_gran(kopt = 5)

### 2021-09-22 supplementary/distance-computation/simulation-data/sim-robust-4iter.Rmd
adding new analaysis

# _Algorithm_
Compute wpd for each granularity.The distance matrix is then computed with 20 time series as cases and three granularities as variables. Manhattan distances are computed and then hierarchical clustering is applied on them.

```{r tab-gran}
design = c("design-1", "design-2", "design-3", "design-4", "design-5")
g1 = c("no", "yes" , "no", "yes", "yes")
g2 = c("no", "no" , "yes", "no", "yes")
g3 = c("no", "yes" , "no", "yes", "yes")
#table <- tibble(design, g1, g2, g3) %>% kable()
#table
```

@@

<!-- Cross-check -->
<!-- data = bind_data_iter %>% filter(design == "design-2", seed_id == 5) -->
<!-- p2 <- ggplot(data, aes(x = as.factor(g1), y = value)) + geom_boxplot() + xlab("g1") + theme_bw() + facet_wrap(~design, ncol = 1) -->
<!-- p3 <- ggplot(data, aes(x = as.factor(g2), y = value)) + geom_boxplot() + xlab("g2") + theme_bw() + facet_wrap(~design, ncol = 1) -->
<!-- p4 <- ggplot(data, aes(x = as.factor(g3), y = value)) + geom_boxplot() + -->
<!-- xlab("g3") + theme_bw() + facet_wrap(~design, ncol = 1) -->
<!-- (p2 + p3 + p4) -->

<!-- ```{r} -->
<!-- p2 <- ggplot(data, aes(x = as.factor(g1), y = value)) + geom_boxplot() + xlab("g1") + theme_bw() -->
<!-- p3 <- ggplot(data, aes(x = as.factor(g2), y = value)) + geom_boxplot() + xlab("g2") + theme_bw() -->
<!-- p4 <- ggplot(data, aes(x = as.factor(g3), y = value)) + geom_boxplot() + -->
<!-- xlab("g3") + theme_bw()  -->
<!-- (p2 + p3 + p4) -->
<!-- ``` -->

>>>>

# _Algorithm_

Robust scaling done for each customer and then JSD is computed between same categories for a granularity.

```{r tab-gran}
design = c("design-1", "design-2", "design-3", "design-4", "design-5")
g1 = c("no", "yes" , "no", "yes", "yes")
g2 = c("no", "no" , "yes", "no", "yes")
g3 = c("no", "yes" , "no", "yes", "yes")
table <- tibble(design, g1, g2, g3) %>% kable()
#table
```

@@

### 2021-09-22 supplementary/effect_transformation.Rmd
adding new analaysis

v2 <- suppressWarnings(robust_scale_data(sm, "hour_day")) %>% 
    dplyr::mutate(kwh_nqt = stats::qqnorm(general_supply_kwh, plot.it=FALSE)$x) %>% 
  mutate(category = as.numeric(category),
         kwh_robust = )

@@

v2 %>%
dplyr::filter(customer_id %in% c("10018250")) %>%
  pivot_longer(c("general_supply_kwh", "scaled_response", "kwh_nqt"),
               names_to = "kwh_type",
               values_to = "kwh_value") %>% ggplot(fill = "#999999") +
  ggridges::geom_density_ridges(aes(x = kwh_value, y = as.factor(category)), alpha = 0.7) +
  facet_grid(kwh_type~customer_id, scales = "free") +
  coord_flip() +
  theme(legend.position = "bottom") +
  theme_bw()

v2 %>%
dplyr::filter(customer_id %in% c("10018250")) %>%
  pivot_longer(c("general_supply_kwh", "scaled_response", "kwh_nqt"),
               names_to = "kwh_type",
               values_to = "kwh_value") %>%
ggplot(aes(x = kwh_value, y = as.factor(category)), fill = "#999999") +
  #ggridges::geom_density_ridges(alpha = 0.7) +
  facet_grid(kwh_type~customer_id, scales = "free") +
  coord_flip() +
  stat_summary(
    fun = quantile_q2,
    geom = 'line',
    aes(group = 1), size = 1, color = "blue") +
  theme(legend.position = "bottom") +
  stat_summary(
    fun = quantile_q1,
    geom = 'line',
    aes(group = 1), size = 1, color = "darkgreen") +
  theme(legend.position = "bottom") +
  stat_summary(
    fun = quantile_q3,
    geom = 'line',
    aes(group = 1), size = 1, color = "#D55E00") +
  theme(legend.position = "bottom") +
  theme_bw()

>>>>

v2 <- suppressWarnings(robust_scale_data(sm, "hour_day")) %>% 
    dplyr::rename( "kwh_robust" = "scaled_response") %>% 
    dplyr::mutate(kwh_nqt = stats::qqnorm(general_supply_kwh, plot.it=FALSE)$x)

C

@@

v2 %>%
dplyr::filter(customer_id %in% c("10018250")) %>%
  pivot_longer(c("general_supply_kwh", "kwh_robust", "kwh_nqt"),
               names_to = "kwh_type",
               values_to = "kwh_value") %>% ggplot(fill = "#999999") +
  ggridges::geom_density_ridges(aes(x = kwh_value, y = as.factor(category)), alpha = 0.7) +
  facet_grid(kwh_type~customer_id, scales = "free") +
  coord_flip() +
  theme(legend.position = "bottom") +
  theme_bw()

v2 %>%
dplyr::filter(customer_id %in% c("10018250")) %>%
  pivot_longer(c("general_supply_kwh", "kwh_robust", "kwh_nqt"),
               names_to = "kwh_type",
               values_to = "kwh_value") %>%
ggplot(aes(x = kwh_value, y = as.factor(category)), fill = "#999999") +
  #ggridges::geom_density_ridges(alpha = 0.7) +
  facet_grid(kwh_type~customer_id, scales = "free") +
  coord_flip() +
  stat_summary(
    fun = quantile_q2,
    geom = 'line',
    aes(group = 1), size = 1, color = "blue") +
  theme(legend.position = "bottom") +
  stat_summary(
    fun = quantile_q1,
    geom = 'line',
    aes(group = 1), size = 1, color = "darkgreen") +
  theme(legend.position = "bottom") +
  stat_summary(
    fun = quantile_q3,
    geom = 'line',
    aes(group = 1), size = 1, color = "#D55E00") +
  theme(legend.position = "bottom") +
  theme_bw()
